---
title: "class6activity"
author: "Mia"
date: "`r Sys.Date()`"
output: html_document
---

## The Bechdel Test
  - there are at least two named women in the picture  
  - they have a conversation with each other at some point  
  - and that conversation isn’t about a male character — 
then it passes "The Rule"


```{r, message = FALSE, warning = FALSE}
install.packages("moderndive", repos = "http://cran.us.r-project.org", dependencies = TRUE)
install.packages("fivethirtyeight", repos = "http://cran.us.r-project.org", dependencies = TRUE)
install.packages("lm.beta", repos = "http://cran.us.r-project.org", dependencies = TRUE)
install.packages("skimr", repos = "http://cran.us.r-project.org", dependencies = TRUE)
install.packages("rstatix", repos = "http://cran.us.r-project.org", dependencies = TRUE)


```


```{r message=FALSE, warning=FALSE}
#options(scipen = 10)
library(moderndive)
library(tidyverse)
library(fivethirtyeight)
library(lm.beta)
library(rstatix)
library(Hmisc)
library(gapminder)

bechdel

```


#create dummy variables
#pass is based on binary variable and coded 1 or 9
# 3 new dummy variables based on clean_test compare each level to 'nowomen'

```{r}
bechdel_recoded <- bechdel %>% 
  mutate(pass = if_else(binary == "PASS", 1, 0))

bechdel_recoded <- bechdel_recoded %>% 
  mutate(
  notalk = if_else(clean_test == "notalk", 1, 0),
  men = if_else(clean_test == "men", 1, 0),
  ok = if_else(clean_test == "ok", 1, 0))

names(bechdel_recoded)




```
  

#regression predicting domestic gross from each level of clean_test
```{r}

model <- lm(domgross_2013 ~ notalk + men + pass, bechdel_recoded)
tidy(lm.beta(model))

```



#mean centering budget and domestic gross so that model parameters are based on the mean values of those predictors instead of 0 (because 0 is less meaningful here)
#running regression on uncentered and centered predictors -- look at how intercept changes
```{r}

bechdel_recoded <- bechdel_recoded %>% 
  mutate(cbudget_2013 = budget_2013 - mean(budget_2013, na.rm = TRUE),
  cdomgross_2013 = domgross_2013 - mean(domgross_2013, na.rm = TRUE))


model <- lm(intgross_2013 ~ budget_2013 + domgross_2013, bechdel_recoded)
tidy(lm.beta(model))

model2 <- lm(intgross_2013 ~ cbudget_2013 + cdomgross_2013, bechdel_recoded)
tidy(lm.beta(model2))


```



