---
title: "candy"
author: "Mia"
date: "`r Sys.Date()`"
output: html_document
---

[https://data.world/fivethirtyeight/candy-power-ranking]

```{r setup, include=FALSE}
install.packages("corrplot", repos = "http://cran.us.r-project.org", dependencies = TRUE)
install.packages("rstatix", repos = "http://cran.us.r-project.org", dependencies = TRUE)
install.packages("lm.beta", repos = "http://cran.us.r-project.org", dependencies = TRUE)
install.packages("generics", repos = "http://cran.us.r-project.org", dependencies = TRUE)
install.packages("fivethirtyeight", repos = "http://cran.us.r-project.org", dependencies = TRUE)

library(corrplot)
library(tidyverse)
library(rstatix)
library(generics)
library(fivethirtyeight)
library(lm.beta)
```

#Recode all true/false as numbers
```{r load_candy}
names(candy_rankings) 
candy_rankings$competitorname
recoded_candy <- candy_rankings %>% mutate(is_caramel = if_else(caramel == TRUE, 1, 0),
                                      is_chocolate = if_else(chocolate == TRUE, 1, 0),
                                      is_fruity = if_else(fruity == TRUE, 1, 0),
                                      is_caramel = if_else(caramel == TRUE, 1, 0),
                                      is_nougat = if_else(nougat == TRUE, 1, 0),
                                      is_peanutyalmondy = if_else(peanutyalmondy == TRUE, 1, 0),
                                      is_crispedricewafer = if_else(crispedricewafer == TRUE, 1, 0),
                                      is_hard = if_else(hard == TRUE, 1, 0),
                                      is_bar = if_else(bar == TRUE, 1, 0),
                                      is_pluribus = if_else(pluribus == TRUE, 1, 0)
                                    )

```


Run a correlation matrix to see overall relationships between variables
But first, we must:
-remove all non-numeric columns

```{r}
candy_corr <- recoded_candy %>% select(-competitorname, -chocolate, -fruity, -caramel, -peanutyalmondy, -nougat, -crispedricewafer, -crispedricewafer, -hard, -bar, -pluribus)

```


Output correlation matrix
```{r}
corrs <- cor_test(short)
corrs
```


run cor() which returns a matrix
create a correlation plot
```{r}
corr_matrix <- cor(short)
corrplot(corr_matrix)
```


Run a regression model with run the model with *is_bar* predicting *winpercent*
Output with standardized coefficient using lm.beta
```{r}
model1 <- lm(winpercent ~ is_bar, recoded_candy)
tidy(lm.beta(model1))
```

output the model statistics
```{r}
glance(model1)
```
Add chocolate to the model
```{r}
model2 <- lm(winpercent ~ is_bar + is_chocolate, recoded_candy)
tidy(lm.beta(model2))
```

Run a model with all of the candy characterisics
```{r}
model3 <- lm(winpercent ~ is_chocolate + is_fruity + is_caramel + is_peanutyalmondy + is_nougat + is_crispedricewafer + is_hard + is_bar + is_pluribus, recoded_candy)
tidy(lm.beta(model3))
```
output model statistics
```{r}
glance(model3)
```
compare models
```{r}
anova(model2, model3)

```

Additional questions:
- Look at the regression model above with all candy characteristics. How would you quantify the relationship between fruity and the outcome (winpercent)?
- What are the top 3 predictors in model3? Based on this, what type of candy would you propose to a candy manufacturer?
- Whether or not a candy was a bar was a positive predictor in the first model but then negative in the full model. Why do you think that happened?
- Is model3 significantly different than model2
- Add pricepercent to the above model and run it. Is it significantly different from the model without?
- Center pricepercent and re-run the model. What is different about the centered versus uncentered models?







