---
title: "contrasts_exercise"
author: "Paola, Kayla, Sijan"
date: "`r Sys.Date()`"
output: html_document
---


CONDITION LEVELS
1- personal me (self-immersed)
2-personal she (self-distance)
3-nonpersonal me (other-immersed)
4-nonpersonal she (other-distance)


article: https://journals.sagepub.com/stoken/default+domain/vIg5KBmaiJHKTXfUpXZK/full
data: https://docs.google.com/spreadsheets/d/1n9k45LeI5ZlwAkazk1RebT1zKbanaPha5iqbYaO0lMM/edit?usp=sharing]

```{r }
library(tidyverse)
library(rstatix)


grossman <- read_csv("grossman_kross.csv")
grossman$CONDITION <- as.factor(grossman$CONDITION)
names(grossman)

```

#plot the means of WISDOM by condition
```{r}
library(ggplot2)
ggplot(grossman, aes(CONDITION, WISDOM))+
  stat_summary(fun="mean", geom="bar")
```


##run ANOVA with WISDOM as DV and CONDITION as IV. Is the overall omnibus test significant? 
```{r}
aov_model <- anova_test(grossman, WISDOM ~ CONDITION, detailed = TRUE)
get_anova_table(aov_model)

```



#Run the following contrasts by replacing the x's in the code chunk below with contrast coefficients.
##Contrast 1: Contrast participants in the self-immersed condition (condition 1) with participants in the other-immersed and other-distanced conditions combined (conditions 3 and 4)
##Contrast 2: Compare self-immersed (condition 1) with self-distance (condition 2)
##Contrast 3: Compare other-immersed (condition 3) with other-distance (condition 4)
##Contrast 4: Compare self-distance (condition 2) with other-immersed and other-distance (conditions 3 and 4)

```{r contrasts}

contrast1 = c(2, 0, -1, -1)
contrast2 = c(1, -1, 0, 0)
contrast3 = c(0, 0, 1, -1)
contrast4 = c(0, 2, -1, -1)

#assign contrasts to condition 
contrasts(grossman$CONDITION) = cbind(contrast1, contrast2, contrast3, contrast4)

#make sure contrasts are assigned correctly
contrasts(grossman$CONDITION)

#run 
m_contrasts <- lm(WISDOM ~ CONDITION, grossman)
summary(m_contrasts)

```

#Write up the one-way ANOVA results in APA style. Write the results of the omnibus test and of the planned contrasts. Did you replicate the authors' findings

<<  >>



##run a posthoc test to compare all conditions to each other
```{r}




```













