---
title: "Lab assignment 3"
author: "Grace, Allama, Shivani and Paola"
date: "2022-10-10"
output: html_document
---


```{r}
library(tidyverse)
library(rstatix)
library(pwr)
```

```{r}
SchroederandEpley2015Experiment4data <- read_csv("~/Desktop/SchroederandEpley2015Experiment4data.csv")
```

```{r}
t.test(Intellect_Rating ~ CONDITION,
  data = SchroederandEpley2015Experiment4data,
  var.equal = FALSE,
  paired = FALSE)

```

```{r}
t.test(Impression_Rating ~ CONDITION,
  data = SchroederandEpley2015Experiment4data,
  var.equal = FALSE,
  paired = FALSE)

```


t.test(Hire_Rating ~ CONDITIONdata:  Intellect_Rating by CONDITION
t = -3.4787, df = 33.434, p-value = 0.001421
alternative hypothesis: true difference in means between group 0 and group 1 is not equal to 0
95 percent confidence interval:
 -3.1481685 -0.8253765
sample estimates:
mean in group 0 mean in group 1
       3.648148        5.634921,
  data = SchroederandEpley2015Experiment4data,
  var.equal = FALSE,
  paired = FALSE)


#just in case you wanted us to know how to use the power function (:
```{r}
library(pwr)
pwr.t.test(n = NULL,
           d = effects,
          sig.level = .05,
          power = .80
          type = "two.sample",
          alternative = "two.sided")
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
