---
title: "repeated measures"
author: "Mia"
date: "`r Sys.Date()`"
output: html_document
---
data: [https://docs.google.com/spreadsheets/d/1OmicmeuzvjiVeGZzeqdbWfIMHpE8FmeBG8t7matWtEE/edit?usp=sharing]
article: [https://journals.sagepub.com/stoken/default+domain/tSMZXMeiaDdnfZ8GbU9y/full]

```{r}
library(tidyverse)
library(lm.beta)
library(rstatix)
```


```{r }
zhang <- read_csv("Zhang et al. 2014 Study 3 - Zhang et al. 2014 Study 3.csv")
```
#rename variables so prefix is consistent
```{r}
zhang <- zhang %>% rename(
                          InterestTime1 = T1_Predicted_Interest_Composite,
                          InterestTime2 = T2_Actual_Interest_Composite
                          )
```

#focus on interest
#create id column
```{r}
interest <- zhang %>% 
  mutate(id = row_number()) %>% 
  select(id, Condition, InterestTime1, InterestTime2) 


view(interest)

 
```

#pivot_longer reshapes from wide to long:
cols = the columns that need to be reshaped (our repeated measure factor)
names_to = new column name for our repeated measure factor
names_prefix = after prefix is the level of our repeated measure factor
values_to = name of the column where the value goes (where to put the value of  InterestTime1, InterestTime2)

```{r}

interest_long <- interest %>% pivot_longer(
  cols = starts_with("InterestTime"),
  names_to = "time",
  names_prefix = "InterestTime",
  values_to = "interest"
)

view(interest_long)

```

anova_test() [rstatix]. Key arguments for performing repeated measures ANOVA:
*data:* data frame
*dv:* (numeric) the dependent (or outcome) variable name.
*wid:* variable name specifying the case/sample identifier.
*within:* within-subjects factor or grouping variable
```{r}

model <- interest_long %>% anova_test( 
                dv = "interest",
                wid = "id",
                within = "time",
                detailed = TRUE
                )
  
get_anova_table(model)

```
```{r}

interest_long %>% 
  group_by(time) %>% 
  get_summary_stats(interest, type = "mean_sd")

```


#now run mixed model
```{r}
model <- interest_long %>% anova_test(  
                dv = "interest",
                wid = "id",
                between = "Condition",
                within = "time",
                detailed = TRUE
                )
    
get_anova_table(model)
```

#run pairwise test of condition at each time point
#correct for multiple tests
condition 1: recall ordinary event
  condition 2: recall extraordinary event
```{r}
pwtest <- interest_long %>%
  group_by(time) %>%
  pairwise_t_test(
    interest ~ Condition, 
    p.adjust.method = "bonferroni",
    )

pwtest
interest_long %>% group_by(time, Condition) %>% get_summary_stats(interest, type = "mean_sd")
  
  

```
Run the same analysis for curiosity. Were participants more or less curious to reread their romantic interactions in predicted (T1) versus actual (T2)?
First run the repeated measures then the mixed model.
How did it differ by condition?
T1_Predicted_Curious	T2_Actual_Curious

#rename variables so prefix is consistent
```{r}
zhang <- zhang %>% rename(
                          CuriousTime1 = T1_Predicted_Curious,
                          CuriousTime2 = T2_Actual_Curious
                          )
```

#focus on curious
#create id column
```{r}
curious <- zhang %>% 
  mutate(id = row_number()) %>% 
  select(id, Condition, CuriousTime1, CuriousTime2) 

view(curious)

```

#pivot_longer reshapes from wide to long:
cols = the columns that need to be reshaped (our repeated measure factor)
names_to = new column name for our repeated measure factor
names_prefix = after prefix is the level of our repeated measure factor
values_to = name of the column where the value goes (where to put the value of  InterestTime1, InterestTime2)

```{r}

curious_long <- curious %>% pivot_longer(
  cols = starts_with("CuriousTime"),
  names_to = "time",
  names_prefix = "CuriousTime",
  values_to = "curiosity"
)

view(curious_long)

```


```{r}

model1 <- curious_long %>% anova_test( 
                dv = "curiosity",
                wid = "id",
                within = "time",
                detailed = TRUE
                )
  
get_anova_table(model1)

```
```{r}

curious_long %>% 
  group_by(time) %>% 
  get_summary_stats(curiosity, type = "mean_sd")

```
Curiosity increased from time 1(M = 3.99, SD = 1.42) to time 2 (M = 4.33, SD = 1.42), F(1, 129) = 5.80, p < 0.0001, eta2[g] = 0.01. 
#now run mixed model
```{r}
model1 <- curious_long %>% anova_test(  
                dv = "curiosity",
                wid = "id",
                between = "Condition",
                within = "time",
                detailed = TRUE
                )
    
get_anova_table(model1)
```

#run pairwise test of condition at each time point
#correct for multiple tests
condition 1: recall ordinary event
  condition 2: recall extraordinary event
```{r}
pwtest1 <- curious_long %>%
  group_by(time) %>%
  pairwise_t_test(
    curiosity ~ Condition, 
    p.adjust.method = "bonferroni",
    )

pwtest1
curious_long %>% group_by(time, Condition) %>% get_summary_stats(curiosity, type = "mean_sd")
```
Were participants more or less curious to reread their romantic interactions in predicted (T1) versus actual (T2)?
First run the repeated measures then the mixed model.
How did it differ by condition?

##### Participants were more curious in actual condition than predicted condition but the difference in curiosity was not significant, F(1, 129) = 0.91, p = 0.34, eta2[g] = 0.005. Participants curiosity increased from time 1 to time 2, F(1, 129) = 6.16, p < 0.01, eta2[g] = 0.015. We also found an effect of time and condition in curiosity level that was significant implying participants were more curious in actual condition than in predicted condition from time 1 to time 2, F(1, 129) = 5.12, p < 0.05, eta2[g] = 0.012.

